NanoMaLy

### 2015-11-19 paper/pldi16-submission/haskellListings.tex
add some keywords
down to 11pp

\usepackage{color}
% uncomment next line to restore colors
% \def\withcolor{}

@@

                target, query, decode, encode, check, refuteSMT, binder,

@@

                padAverage,focusUp,execute,checkSMT,inputTypes,outputType,toReft,app

@@

		module,measure,pred,predicate,of,primitive,then,type,where,lazy,throw,when

>>>>

\usepackage{color}
% uncomment next line to restore colors
\def\withcolor{}

@@

@@

                padAverage,focusUp,execute,checkSMT,inputTypes,outputType,toReft,app,
								genArgs, genWitness, close, witness, mkApps, mkLets, isStuck

@@

		module,measure,pred,predicate,of,primitive,then,type,where,lazy,throw,when,
                rec,function,fun,match,with

### 2015-11-19 paper/pldi16-submission/interactive.tex
down to 11pp

\section{Explaining Type Errors With Traces}
\label{sec:explaining}
%
% We have shown how to reliably find witnesses to type errors in \ocaml,
% but this not fully address our original goal -- to \emph{explain} the
% errors.
% %
% Having identified an input vector that triggers a bug, a common next
% step is to step through the program with a \emph{debugger} to observe
% how the program evolves.
% %
% The existing debuggers and interpreters for \ocaml assume a type-correct
% program, so unfortunately we cannot use them off-the-shelf.
% %
% Instead we return to our semantics for \lang and extend the evaluation
% rules to collect a trace that we can present to the user, demonstrating
% precisely \emph{how} their program went wrong.

@@

In this section we formalize the collection and traversal of the reduction graph.
%
First, we extend our semantics from \S~\ref{sec:semantics} to collect
the edges in the graph (\S~\ref{sec:inter-semant}).
%
Then, we express a set of common debugging steps as graph traversals
(\S~\ref{sec:traversing-graph}).

>>>>

\section{Explaining Type Errors With Traces}
\label{sec:explaining}

A trace, on its own, is likely too detailed to be a good
explanation of the type error. One approach is to use the
witness input to step through the program with a
\emph{debugger} to observe how the program evolves.
%
This route is problematic for two reasons.
%
First, existing debuggers and interpreters for
typed languages (\eg\ \ocaml) typically require
a type-correct program as input.
%
Second, we wish to have a quicker way to get
to the essence of the error, \eg\ by skipping
over irrelevant sub-computations, and focusing
on the important ones.

Next, we present a novel way to debug executions.
%
First, we develop a notion of a
\emph{reduction graph}~(\S~\ref{sec:reduction-graph}).
%
Second, we extend our semantics so that they incrementally
collect the edges in the graph (\S~\ref{sec:inter-semant}).
%
Finally, we express a set of common debugging steps as
graph traversals (\S~\ref{sec:traversing-graph}), yielding
an novel visual interactive debugger that allows the user
to effectively visualize \emph{how} the program goes (wrong.)

@@
